---
title: 'Frontier 1 : Maps'
author: "Claude Grasland"
date: "27/03/2021"
output:
  pdf_document: 
    keep_tex: yes
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message =FALSE, error = FALSE)
library(kableExtra)
library(quanteda)
library(data.table)
library(dplyr)
library(tidyr)
library(ggplot2)
library(sf)
library(cartography)
library(mapsf)
```


## DATA PREPARATION

### Load hypercube

We have collected titles of news declared as *international*  as long as we have depicted the existence of at less one foreign country in the text of the title. In each of the 5 countries, we have selected three newspapers with national audience and available through mediacloud database from mid 2013 to mid 2020. 



```{r}
hc_FRA<-readRDS("corpus/FRA/hc_FRA_states_mobil.Rdata")
hc_FRA<-hc_FRA[who %in%  c("fr_FRA_lmonde", "fr_FRA_figaro","fr_FRA_lacroi"),]
hc_FRA[,.N,list(who)]

hc_DEU<-readRDS("corpus/DEU/hc_DEU_states_mobil.Rdata")
hc_DEU<-hc_DEU[who %in%  c("de_DEU_suddeu", "de_DEU_diewel","de_DEU_frankf"),]
hc_DEU[,.N,list(who)]


hc_GBR<-readRDS("corpus/GBR/hc_GBR_states_mobil.Rdata")
hc_GBR<-hc_GBR[who %in%  c("en_GBR_guardi", "en_GBR_indept","en_GBR_dailyt"),]
hc_GBR[,.N,list(who)]

hc_ITA<-readRDS("corpus/ITA/hc_ITA_states_mobil.Rdata")
hc_ITA<-hc_ITA[who %in%  c("it_ITA_stampa", "it_ITA_repubb","it_ITA_messag"),]
hc_ITA[,.N,list(who)]

hc_ESP<-readRDS("corpus/ESP/hc_ESP_states_mobil.Rdata")
hc_ESP<-hc_ESP[who %in%  c("es_ESP_mundo", "es_ESP_abcxxx","es_ESP_percat"),]
hc_ESP[,.N,list(who)]

hc<-rbind(hc_FRA,hc_DEU,hc_GBR, hc_ITA, hc_ESP)
hc<-hc[order==1,]
```


### Compute news flow between host and guest countries and modelize

What is the distribution of foreign news in each country ? We aggregate news for the whole period by host and guest countries. Then we modelize the expected number of news Fij through a double contrtaint model based on the marginal sums of news produced  by each host country (i) about each guest country (j). Estimation are realized by a **poisson regression model**. 

```{r}
tab<-hc
# Rename variables
tab$host<-substr(tab$who,4,6)
tab$guest<-tab$where1

# count news flow by host-guest countries
tab <- tab[,.(n = round(sum(news),0)), list(guest,host)]

# move from long to wide and back in order to fill missing with 0 
tab<-dcast(tab,guest~host, fill=0,value.var = "n")
tab2<-melt(tab,id.vars = "guest",variable.name = "host",value.name = "Fij")

# Remove internal news
tab2<-tab2[host!=guest,]

# modelize random distribution with double constraint model
model <- glm(data = tab2,
             formula = Fij~guest+host, family = "poisson")

# add estimates
tab2$Eij<-model$fitted.values

# add absolute residuals
tab2$R1ij <-tab2$Fij-tab2$Eij

# add relative residuals
tab2$R2ij <-tab2$Fij/tab2$Eij

# add chi-2 residuals
tab2$R3ij <- (tab2$R1ij*tab2$R1ij)/tab2$Eij
tab2$R3ij[tab2$R1ij<0] <- -tab2$R3ij[tab2$R1ij<0]


# Build wide table

tab1<-dcast(tab2,guest~host, fill=0,value.var = "Fij")
names(tab1)<-c("ISO3","DEU_obs","ESP_obs","FRA_obs","GBR_obs","ITA_obs")
tab1b<-dcast(tab2,guest~host, fill=0,value.var = "Eij")
names(tab1b)<-c("ISO3","DEU_est","ESP_est","FRA_est","GBR_est","ITA_est")
tab1<-merge(tab1,tab1b, by="ISO3")
tab1b<-dcast(tab2,guest~host, fill=0,value.var = "R1ij")
names(tab1b)<-c("ISO3","DEU_res_abs","ESP_res_abs","FRA_res_abs","GBR_res_abs","ITA_res_abs")
tab1<-merge(tab1,tab1b, by="ISO3")
tab1b<-dcast(tab2,guest~host, fill=0,value.var = "R2ij")
names(tab1b)<-c("ISO3","DEU_res_rel","ESP_res_rel","FRA_res_rel","GBR_res_rel","ITA_res_rel")
tab1<-merge(tab1,tab1b, by="ISO3")
tab1b<-dcast(tab2,guest~host, fill=0,value.var = "R3ij")
names(tab1b)<-c("ISO3","DEU_res_chi","ESP_res_chi","FRA_res_chi","GBR_res_chi","ITA_res_chi")
tab1<-merge(tab1,tab1b, by="ISO3")


```

## Prepare world map

We use the world map elaborated by Romain Leconte for his PhD and we choose the full version for centroid and the simplified version for drawing maps. We use a Lambrt Azimuthal Projection centerd on Paris with the formulata *crs = "+proj=laea +x_0=0 +y_0=0 +lon_0=2 +lat_0=49"*. 


```{r}
# Load maps
world_ctr<-st_centroid(st_read("map/world_of_states_2020.shp", quiet =T),of_largest_polygon = T)
world_map<-st_read("map/world_of_states_2020_simplified.shp", quiet=T)


# Project : Lambert Azimuthal - center = Paris
world_ctr = st_transform(world_ctr, 
                           crs = "+proj=laea +x_0=0 +y_0=0 +lon_0=2 +lat_0=49")
world_map= st_transform(world_map, 
                           crs = "+proj=laea +x_0=0 +y_0=0 +lon_0=2 +lat_0=49")

# Merge with observed and estimated values
world_ctr<-merge(world_ctr,tab1,by="ISO3",all.x=T,all.y=F)
world_map<-merge(world_map,tab1,by="ISO3",all.x=T,all.y=F)

```


We try(as an experiment) to use the new package `mapsf` elaborated by RIATE which is the follower of the well known package `cartography`. 

https://riatelab.github.io/mapsf/articles/mapsf.html


```{r}

# import the sample data set
# Initiate a base map
mf_init(x = world_map, theme ="iceberg")

# Plot a shadow
mf_shadow(world_map, add = TRUE,cex = 0.3, col = "lightyellow")



# layout
mf_layout(title = "MAP PROJECTION LAMBERT AZIMUTHAL CENTERED ON PARIS",
          arrow=FALSE,credits = "")

```

---



```{r}

# import the sample data set
# Initiate a base map
mf_init(x = world_map, theme ="iceberg")

# Plot a shadow
mf_shadow(world_map, add = TRUE,cex = 0.3, col = "gray80")

# Plot empty map
mf_map(world_map, type = "base", add = TRUE, border= "white", lwd=0.3)


# plot news by % and rank
world_ctr$size<-100*world_ctr$FRA_obs/sum(world_ctr$FRA_obs,na.rm=T)
world_ctr$rnk<-rank(-world_ctr$size)
world_ctr$top<-cut(world_ctr$rnk, breaks =c(0,5,20,40,80,210))
levels(world_ctr$top) <- c("1-5","6-20","21-40","40-81",">81")
world_ctr$top<-as.character(world_ctr$top)

mf_prop_typo(
  x = world_ctr, 
  var = c("size", "top"), 
  inches = .1, 
  border = "gray20",
  symbol = "circle", 
  col_na = "grey", 
  pal = c("red","orange","yellow","lightyellow","lightgreen"),
  lwd = 0.3,
  leg_pos = c("left", "topleft"),
  leg_title = c("% of news", "rank"),
  leg_title_cex = c(0.7, 0.7),
  leg_val_rnd = 1,
  leg_val_cex = c(.5, .7),
  val_order = c("1-5","6-20","21-40","40-81",">81"),
  leg_no_data = "No data",
  leg_frame = c(FALSE, FALSE),
  add = TRUE
)


# layout
mf_layout(title = "THE WORLD SEEN BY FRENCH NEWSPAPERS (2013-2020)",
          arrow=FALSE,credits = "")

```

```{r}
x<-st_drop_geometry(world_ctr) %>% select("rnk","ISO3","NAME","FRA_obs","size") %>%
  arrange(rnk) %>%
  mutate(cum = cumsum(size))

kable(head(x,15),
                  digits = c(0,0,0,0,1,1),
                  col.names = c("Rank", "Code","Country","Nb.of news","%","Cum. %"),
                   caption = "Top countries mentionned by french newspapers (2013-2020)"
                    )

```

---

```{r}

# import the sample data set
# Initiate a base map
mf_init(x = world_map, theme ="iceberg")

# Plot a shadow
mf_shadow(world_map, add = TRUE,cex = 0.3, col = "gray80")

# Plot empty map
mf_map(world_map, type = "base", add = TRUE, border= "white", lwd=0.3)


# plot news by % and rank
world_ctr$size<-100*world_ctr$DEU_obs/sum(world_ctr$DEU_obs,na.rm=T)
world_ctr$rnk<-rank(-world_ctr$size)
world_ctr$top<-cut(world_ctr$rnk, breaks =c(0,5,20,40,80,210))
levels(world_ctr$top) <- c("1-5","6-20","21-40","40-81",">81")
world_ctr$top<-as.character(world_ctr$top)

mf_prop_typo(
  x = world_ctr, 
  var = c("size", "top"), 
  inches = .1, 
  border = "gray20",
  symbol = "circle", 
  col_na = "grey", 
  pal = c("red","orange","yellow","lightyellow","lightgreen"),
  lwd = 0.3,
  leg_pos = c("left", "topleft"),
  leg_title = c("% of news", "rank"),
  leg_title_cex = c(0.7, 0.7),
  leg_val_rnd = 1,
  leg_val_cex = c(.5, .7),
  val_order = c("1-5","6-20","21-40","40-81",">81"),
  leg_no_data = "No data",
  leg_frame = c(FALSE, FALSE),
  add = TRUE
)


# layout
mf_layout(title = "THE WORLD SEEN BY GERMAN NEWSPAPERS (2013-2020)",
          arrow=FALSE,credits = "")

```

```{r}
x<-st_drop_geometry(world_ctr) %>% select("rnk","ISO3","NAME","DEU_obs","size") %>%
  arrange(rnk) %>%
  mutate(cum = cumsum(size))

kable(head(x,15),
                  digits = c(0,0,0,0,1,1),
                  col.names = c("Rank", "Code","Country","Nb.of news","%","Cum. %"),
                   caption = "Top countries mentionned by german newspapers (2013-2020)"
                    )

```

---

```{r}

# import the sample data set
# Initiate a base map
mf_init(x = world_map, theme ="iceberg")

# Plot a shadow
mf_shadow(world_map, add = TRUE,cex = 0.3, col = "gray80")

# Plot empty map
mf_map(world_map, type = "base", add = TRUE, border= "white", lwd=0.3)


# plot news by % and rank
world_ctr$size<-100*world_ctr$GBR_obs/sum(world_ctr$GBR_obs,na.rm=T)
world_ctr$rnk<-rank(-world_ctr$size)
world_ctr$top<-cut(world_ctr$rnk, breaks =c(0,5,20,40,80,210))
levels(world_ctr$top) <- c("1-5","6-20","21-40","40-81",">81")
world_ctr$top<-as.character(world_ctr$top)

mf_prop_typo(
  x = world_ctr, 
  var = c("size", "top"), 
  inches = .1, 
  border = "gray20",
  symbol = "circle", 
  col_na = "grey", 
  pal = c("red","orange","yellow","lightyellow","lightgreen"),
  lwd = 0.3,
  leg_pos = c("left", "topleft"),
  leg_title = c("% of news", "rank"),
  leg_title_cex = c(0.7, 0.7),
  leg_val_rnd = 1,
  leg_val_cex = c(.5, .7),
  val_order = c("1-5","6-20","21-40","40-81",">81"),
  leg_no_data = "No data",
  leg_frame = c(FALSE, FALSE),
  add = TRUE
)


# layout
mf_layout(title = "THE WORLD SEEN BY BRITISH NEWSPAPERS (2013-2020)",
          arrow=FALSE,credits = "")

```

```{r}
x<-st_drop_geometry(world_ctr) %>% select("rnk","ISO3","NAME","GBR_obs","size") %>%
  arrange(rnk) %>%
  mutate(cum = cumsum(size))

kable(head(x,15),
                  digits = c(0,0,0,0,1,1),
                  col.names = c("Rank", "Code","Country","Nb.of news","%","Cum. %"),
                   caption = "Top countries mentionned by british newspapers (2013-2020)"
                    )

```

---


```{r}

# import the sample data set
# Initiate a base map
mf_init(x = world_map, theme ="iceberg")

# Plot a shadow
mf_shadow(world_map, add = TRUE,cex = 0.3, col = "gray80")

# Plot empty map
mf_map(world_map, type = "base", add = TRUE, border= "white", lwd=0.3)


# plot news by % and rank
world_ctr$size<-100*world_ctr$ESP_obs/sum(world_ctr$ESP_obs,na.rm=T)
world_ctr$rnk<-rank(-world_ctr$size)
world_ctr$top<-cut(world_ctr$rnk, breaks =c(0,5,20,40,80,210))
levels(world_ctr$top) <- c("1-5","6-20","21-40","40-81",">81")
world_ctr$top<-as.character(world_ctr$top)

mf_prop_typo(
  x = world_ctr, 
  var = c("size", "top"), 
  inches = .1, 
  border = "gray20",
  symbol = "circle", 
  col_na = "grey", 
  pal = c("red","orange","yellow","lightyellow","lightgreen"),
  lwd = 0.3,
  leg_pos = c("left", "topleft"),
  leg_title = c("% of news", "rank"),
  leg_title_cex = c(0.7, 0.7),
  leg_val_rnd = 1,
  leg_val_cex = c(.5, .7),
  val_order = c("1-5","6-20","21-40","40-81",">81"),
  leg_no_data = "No data",
  leg_frame = c(FALSE, FALSE),
  add = TRUE
)


# layout
mf_layout(title = "THE WORLD SEEN BY SPANISH NEWSPAPERS (2013-2020)",
          arrow=FALSE,credits = "")

```

```{r}
x<-st_drop_geometry(world_ctr) %>% select("rnk","ISO3","NAME","ESP_obs","size") %>%
  arrange(rnk) %>%
  mutate(cum = cumsum(size))

kable(head(x,15),
                  digits = c(0,0,0,0,1,1),
                  col.names = c("Rank", "Code","Country","Nb.of news","%","Cum. %"),
                   caption = "Top countries mentionned by spanish newspapers (2013-2020)"
                    )

```

---


```{r}

# import the sample data set
# Initiate a base map
mf_init(x = world_map, theme ="iceberg")

# Plot a shadow
mf_shadow(world_map, add = TRUE,cex = 0.3, col = "gray80")

# Plot empty map
mf_map(world_map, type = "base", add = TRUE, border= "white", lwd=0.3)


# plot news by % and rank
world_ctr$size<-100*world_ctr$ITA_obs/sum(world_ctr$ITA_obs,na.rm=T)
world_ctr$rnk<-rank(-world_ctr$size)
world_ctr$top<-cut(world_ctr$rnk, breaks =c(0,5,20,40,80,210))
levels(world_ctr$top) <- c("1-5","6-20","21-40","40-81",">81")
world_ctr$top<-as.character(world_ctr$top)

mf_prop_typo(
  x = world_ctr, 
  var = c("size", "top"), 
  inches = .1, 
  border = "gray20",
  symbol = "circle", 
  col_na = "grey", 
  pal = c("red","orange","yellow","lightyellow","lightgreen"),
  lwd = 0.3,
  leg_pos = c("left", "topleft"),
  leg_title = c("% of news", "rank"),
  leg_title_cex = c(0.7, 0.7),
  leg_val_rnd = 1,
  leg_val_cex = c(.5, .7),
  val_order = c("1-5","6-20","21-40","40-81",">81"),
  leg_no_data = "No data",
  leg_frame = c(FALSE, FALSE),
  add = TRUE
)


# layout
mf_layout(title = "THE WORLD SEEN BY ITALIAN NEWSPAPERS (2013-2020)",
          arrow=FALSE,credits = "")

```

```{r}
x<-st_drop_geometry(world_ctr) %>% select("rnk","ISO3","NAME","ITA_obs","size") %>%
  arrange(rnk) %>%
  mutate(cum = cumsum(size))

kable(head(x,15),
                  digits = c(0,0,0,0,1,1),
                  col.names = c("Rank", "Code","Country","Nb.of news","%","Cum. %"),
                   caption = "Top countries mentionned by italian newspapers (2013-2020)"
                    )

```






```{r}

# import the sample data set
# Initiate a base map
mf_init(x = world_map, theme ="iceberg")

# Plot a shadow
mf_shadow(world_map, add = TRUE,cex = 0.3, col = "lightyellow")


# plot relative residuals
mf_map(
  x = world_map, 
  var = "FRA_res_rel",
  type = "choro",
  breaks = c(0,0.25,0.5,1,2,4,1000),
  pal  = hcl.colors(6, "Green-Orange", rev = FALSE),
  border = "white", 
  lwd = 0.5,
  leg_pos = "topleft", 
  leg_title = "Specialisation index",
  leg_frame =FALSE,
  add = TRUE
) 


# plot residual news
world_ctr$size<-abs(world_ctr$FRA_res_chi)
world_ctr$sign<-as.factor(world_ctr$FRA_res_abs > 0)
levels(world_ctr$sign) <- c("Negative","Positive")

mf_prop_typo(
  x = world_ctr, 
  var = c("size", "sign"), 
  inches = .1, 
  border = "gray20",
  symbol = "circle", 
  col_na = "grey", 
  pal = c("darkorange","darkgreen"),
  lwd = 0.3,
  leg_pos = c("bottomleft", "left"),
  leg_title = c("Residuals Chi-2", "Residuals sign"),
  leg_title_cex = c(0.7, 0.7),
  leg_val_cex = c(.7, .7),
  val_order = c("Positive", "Negative"),
  leg_no_data = "No data",
  leg_frame = c(FALSE, FALSE),
  add = TRUE
)


# layout
mf_layout(title = "SPECIFIC FOCUS OF FRENCH NEWSPAPERS (2013-2020)",
          arrow=FALSE,credits = "")

```

```{r}
x<-st_drop_geometry(world_ctr) %>% select("ISO3","NAME","FRA_obs","FRA_est","FRA_res_abs","FRA_res_rel","FRA_res_chi") %>%
  arrange(-FRA_res_chi)

kable(head(x,15),
                  digits = c(0,0,0,0,0,2,1),
                  col.names = c("Code","Country","Observed","Estimated","Difference","Ratio","Chi-square"),
                  row.names = 1:20,
                   caption = "Most significant positive residuals of French Newspapers"
                    )

```


---

```{r}

# import the sample data set
# Initiate a base map
mf_init(x = world_map, theme ="iceberg")

# Plot a shadow
mf_shadow(world_map, add = TRUE,cex = 0.3, col = "lightyellow")


# plot relative residuals
mf_map(
  x = world_map, 
  var = "DEU_res_rel",
  type = "choro",
  breaks = c(0,0.25,0.5,1,2,4,1000),
  pal  = hcl.colors(6, "Green-Orange", rev = FALSE),
  border = "white", 
  lwd = 0.5,
  leg_pos = "topleft", 
  leg_title = "Specialisation index",
  leg_frame =FALSE,
  add = TRUE
) 


# plot residual news
world_ctr$size<-abs(world_ctr$DEU_res_chi)
world_ctr$sign<-as.factor(world_ctr$DEU_res_abs > 0)
levels(world_ctr$sign) <- c("Negative","Positive")

mf_prop_typo(
  x = world_ctr, 
  var = c("size", "sign"), 
  inches = .1, 
  border = "gray20",
  symbol = "circle", 
  col_na = "grey", 
  pal = c("darkorange","darkgreen"),
  lwd = 0.3,
  leg_pos = c("bottomleft", "left"),
  leg_title = c("Residuals Chi-2", "Residuals sign"),
  leg_title_cex = c(0.7, 0.7),
  leg_val_cex = c(.7, .7),
  val_order = c("Positive", "Negative"),
  leg_no_data = "No data",
  leg_frame = c(FALSE, FALSE),
  add = TRUE
)


# layout
mf_layout(title = "SPECIFIC FOCUS OF GERMAN NEWSPAPERS (2013-2020)",
          arrow=FALSE,credits = "")

```



```{r}
x<-st_drop_geometry(world_ctr) %>% select("ISO3","NAME","DEU_obs","DEU_est","DEU_res_abs","DEU_res_rel","DEU_res_chi") %>%
  arrange(-DEU_res_chi)

kable(head(x,15),
                  digits = c(0,0,0,0,0,2,1),
                  col.names = c("Code","Country","Observed","Estimated","Difference","Ratio","Chi-square"),
                  row.names = 1:20,
                  caption = "Most significant positive residuals of German Newspapers"
                    )

```


---


```{r}

# import the sample data set
# Initiate a base map
mf_init(x = world_map, theme ="iceberg")

# Plot a shadow
mf_shadow(world_map, add = TRUE,cex = 0.3, col = "lightyellow")


# plot relative residuals
mf_map(
  x = world_map, 
  var = "GBR_res_rel",
  type = "choro",
  breaks = c(0,0.25,0.5,1,2,4,1000),
  pal  = hcl.colors(6, "Green-Orange", rev = FALSE),
  border = "white", 
  lwd = 0.5,
  leg_pos = "topleft", 
  leg_title = "Specialisation index",
  leg_frame =FALSE,
  add = TRUE
) 


# plot residual news
world_ctr$size<-abs(world_ctr$GBR_res_chi)
world_ctr$sign<-as.factor(world_ctr$GBR_res_abs > 0)
levels(world_ctr$sign) <- c("Negative","Positive")

mf_prop_typo(
  x = world_ctr, 
  var = c("size", "sign"), 
  inches = .1, 
  border = "gray20",
  symbol = "circle", 
  col_na = "grey", 
  pal = c("darkorange","darkgreen"),
  lwd = 0.3,
  leg_pos = c("bottomleft", "left"),
  leg_title = c("Residuals Chi-2", "Residuals sign"),
  leg_title_cex = c(0.7, 0.7),
  leg_val_cex = c(.7, .7),
  val_order = c("Positive", "Negative"),
  leg_no_data = "No data",
  leg_frame = c(FALSE, FALSE),
  add = TRUE
)


# layout
mf_layout(title = "SPECIFIC FOCUS OF BRITISH NEWSPAPERS (2013-2020)",
          arrow=FALSE,credits = "")

```

```{r}
x<-st_drop_geometry(world_ctr) %>% select("ISO3","NAME","GBR_obs","GBR_est","GBR_res_abs","GBR_res_rel","GBR_res_chi") %>%
  arrange(-GBR_res_chi)

kable(head(x,15),
                  digits = c(0,0,0,0,0,2,1),
                  col.names = c("Code","Country","Observed","Estimated","Difference","Ratio","Chi-square"),
                  row.names = 1:20,
                  caption = "Most significant positive residuals of British Newspapers"
                    )

```


---


```{r}

# import the sample data set
# Initiate a base map
mf_init(x = world_map, theme ="iceberg")

# Plot a shadow
mf_shadow(world_map, add = TRUE,cex = 0.3, col = "lightyellow")


# plot relative residuals
mf_map(
  x = world_map, 
  var = "ESP_res_rel",
  type = "choro",
  breaks = c(0,0.25,0.5,1,2,4,1000),
  pal  = hcl.colors(6, "Green-Orange", rev = FALSE),
  border = "white", 
  lwd = 0.5,
  leg_pos = "topleft", 
  leg_title = "Specialisation index",
  leg_frame =FALSE,
  add = TRUE
) 


# plot residual news
world_ctr$size<-abs(world_ctr$ESP_res_chi)
world_ctr$sign<-as.factor(world_ctr$ESP_res_abs > 0)
levels(world_ctr$sign) <- c("Negative","Positive")

mf_prop_typo(
  x = world_ctr, 
  var = c("size", "sign"), 
  inches = .1, 
  border = "gray20",
  symbol = "circle", 
  col_na = "grey", 
  pal = c("darkorange","darkgreen"),
  lwd = 0.3,
  leg_pos = c("bottomleft", "left"),
  leg_title = c("Residuals Chi-2", "Residuals sign"),
  leg_title_cex = c(0.7, 0.7),
  leg_val_cex = c(.7, .7),
  val_order = c("Positive", "Negative"),
  leg_no_data = "No data",
  leg_frame = c(FALSE, FALSE),
  add = TRUE
)


# layout
mf_layout(title = "SPECIFIC FOCUS OF SPANISH NEWSPAPERS (2013-2020)",
          arrow=FALSE,credits = "")

```


```{r}
x<-st_drop_geometry(world_ctr) %>% select("ISO3","NAME","ESP_obs","ESP_est","ESP_res_abs","ESP_res_rel","ESP_res_chi") %>%
  arrange(-ESP_res_chi)

kable(head(x,15),
                  digits = c(0,0,0,0,0,2,1),
                  col.names = c("Code","Country","Observed","Estimated","Difference","Ratio","Chi-square"),
                  row.names = 1:20,
                  caption = "Most significant positive residuals of Spanish Newspapers"
                    )

```


---


```{r}

# import the sample data set
# Initiate a base map
mf_init(x = world_map, theme ="iceberg")

# Plot a shadow
mf_shadow(world_map, add = TRUE,cex = 0.3, col = "lightyellow")


# plot relative residuals
mf_map(
  x = world_map, 
  var = "ITA_res_rel",
  type = "choro",
  breaks = c(0,0.25,0.5,1,2,4,1000),
  pal  = hcl.colors(6, "Green-Orange", rev = FALSE),
  border = "white", 
  lwd = 0.5,
  leg_pos = "topleft", 
  leg_title = "Specialisation index",
  leg_frame =FALSE,
  add = TRUE
) 


# plot residual news
world_ctr$size<-abs(world_ctr$ITA_res_chi)
world_ctr$sign<-as.factor(world_ctr$ITA_res_abs > 0)
levels(world_ctr$sign) <- c("Negative","Positive")

mf_prop_typo(
  x = world_ctr, 
  var = c("size", "sign"), 
  inches = .1, 
  border = "gray20",
  symbol = "circle", 
  col_na = "grey", 
  pal = c("darkorange","darkgreen"),
  lwd = 0.3,
  leg_pos = c("bottomleft", "left"),
  leg_title = c("Residuals Chi-2", "Residuals sign"),
  leg_title_cex = c(0.7, 0.7),
  leg_val_cex = c(.7, .7),
  val_order = c("Positive", "Negative"),
  leg_no_data = "No data",
  leg_frame = c(FALSE, FALSE),
  add = TRUE
)


# layout
mf_layout(title = "SPECIFIC FOCUS OF ITALIAN NEWSPAPERS (2013-2020)",
          arrow=FALSE,credits = "")

```


```{r}
x<-st_drop_geometry(world_ctr) %>% select("ISO3","NAME","ITA_obs","ITA_est","ITA_res_abs","ITA_res_rel","ITA_res_chi") %>%
  arrange(-ITA_res_chi)

kable(head(x,15),
                  digits = c(0,0,0,0,0,2,1),
                  col.names = c("Code","Country","Observed","Estimated","Difference","Ratio","Chi-square"),
                  row.names = 1:20,
                  caption = "Most significant positive residuals of Italian Newspapers"
                    )

```

---
