---
title: 'Frontier 1 : Corpus description'
author: "Claude Grasland"
date: "27/03/2021"
output:
  pdf_document: 
    keep_tex: yes
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
library(quanteda)
library(data.table)
library(dplyr)
library(tidyr)
library(ggplot2)
```



## Corpus description

We have collected titles of news declared as *international*  as long as we have depicted the existence of at less one foreign country in the text of the title. In each of the 5 countries, we have selected three newspapers with national audience and available through mediacloud database from mid 2013 to mid 2020. 



```{r}
hc_FRA<-readRDS("corpus/FRA/hc_FRA_states_mobil.Rdata")
hc_FRA<-hc_FRA[who %in%  c("fr_FRA_lmonde", "fr_FRA_figaro","fr_FRA_lacroi"),]
hc_FRA[,.N,list(who)]

hc_DEU<-readRDS("corpus/DEU/hc_DEU_states_mobil.Rdata")
hc_DEU<-hc_DEU[who %in%  c("de_DEU_suddeu", "de_DEU_diewel","de_DEU_frankf"),]
hc_DEU[,.N,list(who)]


hc_GBR<-readRDS("corpus/GBR/hc_GBR_states_mobil.Rdata")
hc_GBR<-hc_GBR[who %in%  c("en_GBR_guardi", "en_GBR_indept","en_GBR_dailyt"),]
hc_GBR[,.N,list(who)]

hc_ITA<-readRDS("corpus/ITA/hc_ITA_states_mobil.Rdata")
hc_ITA<-hc_ITA[who %in%  c("it_ITA_stampa", "it_ITA_repubb","it_ITA_messag"),]
hc_ITA[,.N,list(who)]

hc_ESP<-readRDS("corpus/ESP/hc_ESP_states_mobil.Rdata")
hc_ESP<-hc_ESP[who %in%  c("es_ESP_mundo", "es_ESP_abcxxx","es_ESP_percat"),]
hc_ESP[,.N,list(who)]

hc<-rbind(hc_FRA,hc_DEU,hc_GBR, hc_ITA, hc_ESP)
hc<-hc[order==1,]
```



### Table 1 :  news by media and year

Distribution is reasonably homogeneous. number of news is divided in two in 2013 and 2020 because only half a year was collected. 

```{r}
tab <- hc 
tab$year<-substr(as.character(tab$when),1,4)
tab<-tab[is.na(tab$year)==F]
tab <- tab[,.(n = round(sum(news),0)), list(year,who)]
tab<-dcast(tab,who~year, fill=0)
mat<-as.matrix(tab[,-1])
row.names(mat)<-tab$who
tabfin <- addmargins(mat)
kable(tabfin)


```



### Figure 1 : news by country and month

```{r}
tab <- hc 
tab$month<-cut(tab$when,breaks = "month")
tab$country<-substr(tab$who,4,6)
tab <- tab[,.(n = round(sum(news),0)), list(month,country)]
tab$month<-as.Date(tab$month)
p <- ggplot(tab, aes(x=month, y = n,colour=country)) +
      geom_line() +
      ggtitle("Total number of foreign news by host country",
              subtitle = "Source : Mediacloud")
p
ggsave(plot=p, filename = "fig_news_country_month.pdf")

```

## World coverage

What is the distribution of foreign news in each country ?



```{r}
tab<-hc
tab <- tab[,.(n = round(sum(news),0)), list(where1,who)]
tab<-dcast(tab,where1~who, fill=0)
mat<-as.matrix(tab[,-1])
row.names(mat)<-tab$where1
```


### Correspondance Analysis

```{r}
library(FactoMineR)
library(explor)
mat2<-mat[!rownames(mat) %in% c("FRA","GBR","DEU","ITA","ESP"),]
afc <- CA(mat2,graph = FALSE)
#explor(afc)
```
### Cluster Analysis / host

```{r}
cah1 <- HCPC(afc,cluster.CA = "columns",nb.clust = 5, graph = F)
plot.HCPC(cah1, choice = "tree",title = "Clustering of newspaper")

pdf(file = "Fig_cluster_media.pdf")
plot.HCPC(cah1, choice = "tree",title = "Clustering of newspaper")
dev.off()
```

### Cluster Analysis / guest

```{r}
cah2 <- HCPC(afc,cluster.CA = "rows",nb.clust = 6, graph = F)
plot.HCPC(cah2, choice = "tree",title = "Clustering of guest countries")
x<-cah2$data.clust

tab<-x %>% group_by(clust) %>% summarise_all(.funs = sum)
tabcont<-as.data.frame(tab[,-1])
row.names(tabcont)<-tab$clust
tabcont<-as.matrix(tabcont)
colnames(tabcont)<-substr(colnames(tabcont),1,2)


library(vcd)
mosaicplot(tabcont,shade = T)

```


```{r} 
library(sf)
library(cartography)
map<-st_read("map/world_of_states_2020.shp")
don<-cah2$data.clust
don$ISO3<-row.names(don)
mapdon<-merge(map,don,by="ISO3",all.x=T,all.y=F)


mapdon$typo<-as.factor(mapdon$clust)
levels(mapdon$typo)
levels(mapdon$typo) <-c("1.UK",
                        "2.UK & France",
                        "3.Germany & Italy",
                        "4.Italy & France",
                        "1.France",
                        "6.Spain")
par(mar=c(0,0,0,0))
typoLayer(mapdon,var ="typo",
          col = c("pink","lightblue","orange","lightgreen","blue","lightyellow"))


pdf("map_typo_guest.pdf")
mapdon$typo<-as.factor(mapdon$clust)
levels(mapdon$typo)
levels(mapdon$typo) <-c("1.UK",
                        "2.UK & France",
                        "3.Germany & Italy",
                        "4.Italy & France",
                        "1.France",
                        "6.Spain")
par(mar=c(0,0,0,0))
typoLayer(mapdon,var ="typo",
          col = c("pink","lightblue","orange","lightgreen","blue","lightyellow"))
dev.off()



```
